White Stork Antimicrobial Resistance

### 2023-03-17 1 Data Cleaning Script/DataCleaningScript.qmd
Project Reorganization
McKay et al 2020 used as a reference

```{r, message=FALSE, warning=FALSE}
#load in data
stork_AMR_raw <- read_csv(here::here("data","raw_data","StorkAMRraw_2020_2021.csv"))
```

@@

```{r}
save_data_location <- here::here("data","processed_data","stork_AMR_2021.rds")
saveRDS(stork_AMR_2021, file = save_data_location)

save_data_location2 <- here::here("data","processed_data","stork_AMR_clean.rds")
saveRDS(stork_AMR_clean, file = save_data_location2)
```

>>>>

```{r, message=FALSE, warning=FALSE}
#load in data
stork_AMR_raw <- read_csv(here::here("1 Data Cleaning Script","raw_data","StorkAMRraw_2020_2021.csv"))
```

@@

```{r}
save_data_location <- here::here("2 Clean Data","stork_AMR_2021.rds")
saveRDS(stork_AMR_2021, file = save_data_location)

save_data_location2 <- here::here("2 Clean Data","stork_AMR_clean.rds")
saveRDS(stork_AMR_clean, file = save_data_location2)
```

### 2023-03-17 3 Analysis Scripts/Data_Exploratory_Analysis.qmd
Project Reorganization
McKay et al 2020 used as a reference

```{r}
#load all data
stork_AMR_clean <- readRDS(here::here("data","processed_data","stork_AMR_clean.rds"))

#load 2021 data
stork_AMR_2021 <- readRDS(here::here("data","processed_data","stork_AMR_2021.rds"))

>>>>

```{r}
#load all data
stork_AMR_clean <- readRDS(here::here("2 Clean Data","stork_AMR_clean.rds"))

#load 2021 data
stork_AMR_2021 <- readRDS(here::here("2 Clean Data","stork_AMR_2021.rds"))
